Automated Topic Naming

### 2012-01-18 ese/ese.tex
abstract attempt

Researchers have employed a variety of techniques to extract underlying
topics that relate to software development artifacts.  Typically, these
techniques use semi-unsupervised machine-learning algorithms to suggest
candidate word-lists.  However, word-lists are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  Latent Dirichlet Allocation (LDA) from commit-log comments recovered
from source control systems. % such as CVS and BitKeeper.  
These topics are given labels from a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on three large-scale Relational Database Management System (RDBMS) projects: MySQL, PostgreSQL and MaxDB.  
The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels relevant to these projects, which provides fresh
insight into their evolving software development activities.
%160 words
\keywords{ Software maintenance \and Repository mining \and Latent Dirichlet allocation \and Topic models}

>>>>

%Researchers have employed a variety of techniques to extract underlying
%topics that relate to software development artifacts.  Typically, these
%techniques use semi-unsupervised machine-learning algorithms to suggest
%candidate word-lists, topics.  
Software repositories provide a deluge of software artifacts to
analyze. Researchers have attempted to summarize, categorize, and relate these
artifacts by using semi-unsupervised machine-learning
algorithms, such as Latent Dirichlet Allocation (LDA), used for concept and topic analysis to suggest candidate
word-lists or topics that describe and relate software artifacts.
However, these word-lists and topics are
difficult to 
interpret in the absence of meaningful summary labels.  Current topic modeling 
techniques assume manual labelling and do not use domain-specific knowledge
to improve, contextualize, or describe results for the developers.  
We propose a solution: \emph{automated labelled topic extraction}.
  Topics are extracted 
using  LDA from commit-log comments recovered
from source control systems. % such as CVS and BitKeeper.  
These topics are given labels from a generalizable
cross-project taxonomy, consisting of non-functional
requirements. Our approach was evaluated with experiments and case studies
on three large-scale Relational Database Management System (RDBMS) projects: MySQL, PostgreSQL and MaxDB.  
The case studies
show that labelled topic extraction can produce appropriate,
context-sensitive labels relevant to these projects, which provides fresh
insight into their evolving software development activities.
%160 words
\keywords{ Software maintenance \and Repository mining \and Latent Dirichlet allocation \and Topic models}
